
%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{\faCc\acvHeaderIconSep Side Projects \& Open Source Contributions}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {The Backend \& API Developer} % Job title
    {Umrah For Them} % Organization
    {\href{https://github.com/mtantawy/UmrahForThemBackend} {github.com/mtantawy}} % Location
    {\href{http://umrah4them.com} {umrah4them.com}} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Laravel 5.1 based backend and API for mobile apps that allow Muslims to perform prayers at Mekkah for the deceased.}
        \item {RESTful APIs for iOS and Android apps, using OAuth 2.0 for authentication.}
        \item {Help families of the deceased to add them including some basic info about the deceased.}
        \item {Users who are at Mekkah, choose from the deceased list to perform Umrah/prayers for them and either cancel or mark as done.}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {Contributor} % Job title
    {CurrantPi - Keep an eye on your Raspberry Pi with zero configuration} % Organization
    {\href{http://github.com/ColinWaddell/CurrantPi} {github.com/ColinWaddell/CurrantPi}} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {A simple web app that shows info about the Raspberry Pi it is running on, like, temperature, network, uptime, cpu load, memory, and storage.}
        \item {Helped re-structuring the app for better maintainability.}
        \item {Added an API that shows all the info but in JSON format, to allow for further extending the app by developing different interface.}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {Contributor} % Job title
    {Magento 2 Samples - Code samples for Magento developers} % Organization
    {\href{https://github.com/magento/magento2-samples} {github.com/magento/magento2-samples}} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Fixed many issues in one of the samples that were rendering it completely not working.}
        \item {Pull Request still pending, but confirmed to be working by other users having same issues with the sample.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}

