
%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{\faCubes\acvHeaderIconSep Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {robusta studio} % Job title
    {B.TECH: MiniCash Partners App} % Organization
    {internal system} % Location
    {web app and APIs} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Laravel 5.2 based web app and APIs for mobile apps, LEMP stack with latest PHP7, MySQL 5.7, Nginx 1.11.1, and OAuth2.0-based authentication.}
        \item {System allows retailers to use B.TECH's MiniCash system to allow customers to pay by installments.}
        \item {Unit Tests for APIs using PHPUnit.}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {robusta studio} % Job title
    {B.TECH: E-Commerce Platform} % Organization
    {\href{http://www.btech.eg} {btech.eg}} % Location
    {ecommerce} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {E-commerce multilingual store built with Magento Enterprise 2.0.7.}
        \item {Optimized Best Sellers calculation.}
        \item {Integration with \href{http://www.etilize.com} {GfK Etilize} for importing products with all attributes and images.}
        \item {Batch imports supporting updates with duplicates for products, categories, attributes, and attribute values.}
        \item {Custom develoepd system for customers to pay by installments ``MiniCash".}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {robusta studio} % Job title
    {Raya Shop} % Organization
    {\href{http://www.rayashop.com} {rayashop.com}} % Location
    {ecommerce} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {E-commerce multilingual store built with Magento Enterprise 1.14, managing 20,000+ products, 40,000+ customers, and 50,000+ daily visits.}
        \item {Optimized Best Sellers calculation which decreased load time by more than 10x under huge traffic.}
        \item {Optimized theme, re-implemented various parts, and decreased load time by about 10x.}
        \item {Integrated with Microsoft RMS for products, prices, and stock management.}
        \item {Integrated with payment gateways, SMS gateway, Mandrill , and Shipping carrier ``Aramex".}
        \item {Integrated with Raya systems, like, Installments, Elite/Loyalty points, and After Sales system.}
        \item {Custom reports and API for daily summarized custom report for executives.}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {robusta studio} % Job title
    {IQSAN LMS (Learning Management System)} % Organization
    {\href{http://www.iqsanlms.com} {iqsanlms.com}} % Location
    {web app} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Laravel 5.1 based web app, supports multiple schools where each school can add teachers, students, parents, and rest of the school staff.}
        \item {Google Calendar-like events calendar per school, stage, and class, with filters like event type and courses.}
        \item {Internal messaging system where users can communicate either one-to-one or one-to-many.}
        \item {Complaint system for students and parents to be able to communicate with complaint officer(s) and escalate to stage or school principal.}
        \item {RESTful APIs for iOS and Android apps, using OAuth 2.0 for authentication, and MongoDB for web and mobile/push notifications.}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {robusta studio} % Job title
    {Beqala} % Organization
    {\href{http://www.beqala.com} {beqala.com}} % Location
    {ecommerce} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Online Supermarket with a nice experience and delivery options, based on highly customized WooCommerce over WordPress.}
        \item {Custom search plugin to provide enhanced search results and increase conversion rate.}
        \item {Optimized PHP and MySQL configurations which decreased load time by 2x under real traffic.}
        \item {Integrated with payment gateways, and ERP system for products, prices, stock, customers, and orders management.}
        \item {Shopping List that automatically find best products that match customer's list, and a custom ``pickup from store" plugin.}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {robusta studio} % Job title
    {GS1 Egypt} % Organization
    {\href{http://www.gs1eg.org} {gs1eg.org}} % Location
    {website} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Informative WordPress-based website for Egypt's branch of GS1, the global barcode provider.}
        \item {Built according to strict branding standards of GS1 international.}
        \item {Customized theme and plugins, specially ``Visual Composer" blocks.}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {ASSET Technology Group} % Job title
    {SCCI (Sharjah Chamber of Commerce and Industry)} % Organization
    {internal system} % Location
    {web app} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {SCCI in UAE is responsible for ``Membership Registration \& Renewal", and issuing ``Certificates of Origin \& Attestations".}
        \item {Currently, the system processes about a thousand requests daily in different branches of the chamber and website.}
        \item {Technologies, \& Database used: Java/JSPs/Servlets/jBoss application server/jBoss work flows/ jQuery/JAX-WS/SQL Server 2008.}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {ASSET Technology Group} % Job title
    {DTC (Dubai Taxi Corporation)} % Organization
    {internal system} % Location
    {web app} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {The system manages driver's info, staff info, fuel cards, and work flows for HR.}
        \item {Workflows including recruitment, vacation requests, issuing new fuel cards, and others.}
        \item {Technologies, \& Databases used: Java/JSPs/jBoss application server/jBoss work flows/jQuery/JAX-WS/SQL Server 2008/MySQL/Oracle.}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {Ain Shams University, Faculty of Engineering} % Job title
    {SSH (Secure Smart Home)} % Organization
    {graduation project} % Location
    {hardware product} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {As IoT (Internet of Things) devices spread, the need for security increases, we investigated security on all layers.}
        \item {Focus on securing the Linux environment through permissions, iptables, and integrity checks on bootup.}
        \item {Built on embedded system boards ``BeagleBone" \& ``Arduino", core developed using Python, web interface using PHP, all with security in mind.}
      \end{cvitems}
    }


%---------------------------------------------------------
\end{cventries}

